Estimation of cloud-corrected microwave humidity radiances with associated uncertainties

### 2020-11-16 Article/ici_submm_cloudcorr.tex
added calibration plot ECMWF error model,  small modifications in text

\Author[1]{Inderpreet}{Kaur}
\Author[1]{Patrick}{Eriksson}
\Author[1]{Simon}{Pfreundschuh}
\Author[2]{David}{Duncan}

@@

%Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds. The residual cloud impact can have some drawbacks. 
At 183\,GHz, the impact of hydrometeors typically causes a decrease in the observed radiance due to scattering from ice hydrometeors (e.g.\ \citet{barlakas:three:20}). This implies that if any cloud contamination is missed by the filtering, a negative bias in mean radiance will result compared to the true clear-sky mean, which may translate into a bias in humidity after the retrieval or assimilation. For NWP systems assimilating clear-sky observations, the effect of undetected clouds may be overcome by inflating the observational errors and diminishing the impact of observations. Furthermore, the mathematical assumptions of data assimilation are predicated on Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction. One solution is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data. Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected. This often rejects more observations than needed, as the channels differ in their altitude coverage. An observation could be cloudy in some channels and still the be clear-sky in others. To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression would be best as the ideal solution would be scene-dependent. This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}. A maybe less obvious problem is the assignment of uncertainty to the filtered values. To our best knowledge, so far only estimates of mean and worst case errors exist in the literature. Some cases with relatively high cloud impact will likely be missed, while most cases are clear-sky from the start. As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate. However, this will unnecessarily downgrade the value of the truly clear-sky cases and the observations are used in a non-optimal manner.

@@

The main focus of this study is the potential of this cloud-correction
method using sub-millimetre (sub-mm) observations, which will become available
operationally with the launch of the Ice Cloud Imager (ICI,
\citet{eriksson:towar:20}) on board the next generation of EUMETSAT Polar System - Second Generation (EPS-SG), but will likely also be included in
several smaller missions (such as Artic Weather Satellite (AWS); presented
below). Additionally, we demonstrate the feasibility of the approach based on
observations at 89 and 150\ GHz channels (following
\citet{geer2015scatteringindex}), which are available on several sensors extant today. The focus
on sub-mm channels is motivated by several reasons. First, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors and are thus expected to provide greater sensitivity to high altitude cirrus clouds. For example, in some cloudy situations the
cloud impact at 183\,GHz may be of the order of thermal noise and modelling uncertainties,
while the impact at 325\,GHz is significant enough to provide sufficient signal to noise for identifying cloud. Second, the proposed
cloud correction methods allow integration of ICI sub-mm observations in
clear-sky data assimilation schemes with no further modifications, thus providing a simple
way to make use this novel data source as soon as it becomes available.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}. The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.

@@

\subsubsection{Ice Cloud Imager}
%
%t
\begin{table}[t]	
	\caption{Specifications of ICI channels relevant to this study.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	\\
				& [GHz]			& [MHz]			& [K]			\\
		\middlehline
		I1V&	183.31$\pm$7.00    & 2000 			& 0.8 		\\
		I2V&	183.31$\pm$3.40    & 1500 			& 0.8 		\\
		I3V&	183.31$\pm$2.00    & 1500			& 0.8 		\\
		I5V&	325.15$\pm$9.50    & 3000			& 1.2 		\\
		I6V&	325.15$\pm$3.50    & 2400			& 1.3 		\\
		I6V&	325.15$\pm$1.50    & 1600			& 1.5 		\\
		I8V&	448.00$\pm$7.20    & 3000			& 1.4 		\\
		I9V&	448.00$\pm$3.00    & 2000			& 1.6 		\\
		I10V&	448.00$\pm$1.40    & 1200			& 2.0 		\\
		I11V&	664.00$\pm$4.20    & \phantom{0}500	& 1.6 		\\		
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation). MetOp-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties, and improve the representation of ice clouds in regional and global NWP models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.  Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\unit{^{\degree}}$(measured from nadir). For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs. Therefore, a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}). CloudSat\citep{Stephens2002cloudsat} profiles from August 2015 are randomly selected for forward simulations. The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 140\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 were used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for AWS. 120\,000 simulations are used for training and the rest are used for testing.

@@

	\item QRNN-all: Same as QRNN-single, but all available 183\,GHz frequencies are included.      
\end{enumerate}

@@

All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset. The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}). The validation dataset is part of the training dataset which is held back during the training process.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{The distribution of point estimate $\ynfcs$ obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
	\caption{The error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown. }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
		\middlehline
Bias     &  0.00 &  -0.84 & -0.10 & -0.09 & -0.05 & -0.04 & -0.11 & -0.10 & -0.10 & -0.09 & 0.24  & -0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness & -0.02 & -12.72 & -1.17 & -1.00 & -1.06 & -0.90 & -1.16 & -1.04 & -1.78 & -1.71 &-1.95  & -3.45\\
Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.8\%& 3.5\%\\
\bottomhline
	\end{tabular}
\end{table*}

The posterior distribution of $\ynfcs$ obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V}. The median value is chosen as the point estimate (see Sect.~\ref{sec:validation}). The distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are corrected successfully with QRNN (blue curve), but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-12.72) and high bias (-0.84\,K). QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.10\,K. However, high skewness values indicate a negative tail or uncorrected departures. Including 118\,GHz in the training gives comparable results as 89+150\,GHz. With 118\,GHz, the error distribution has lower bias and are more symmetric, but the MAE and STD remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz.

Further, we investigated whether filtering the predictions with low accuracy could help in improving the error distributions. For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are associated with large deviations. In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed. With 5\,K threshold, though the cases with high errors are removed, the persistent negative skewness indicates presence of cases with residual cloud impact. Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.

In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}. SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases. They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ \,GHz and $183.31\pm 1.00$ \,GHz as a measure of cloud impact. Further in the text we refer this filter as ``B183''. The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}. With SI threshold = 5\,K, almost 28\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN. The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear. Similar is the case with B183. Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI. The results from the two filters are not surprising as both aim at removing only cases with high ice content. The thin cirrus clouds and other low hydrometeor impact cases remain unaltered.

The three experiments were also performed for other four 183\,GHz channels, and a similar performance was obtained (Table not shown). The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed. The results for these channels with combination 89+150\,GHz are provided in Sect.~\ref{sec:mwhs_others}

>>>>

\Author[1]{Inderpreet}{Kaur}
\Author[1]{Patrick}{Eriksson}
\Author[1]{Simon}{Pfreundschuh}
\Author[2]{David Ian}{Duncan}

@@

%Despite their broad usage, these filtering methods aim at partial removal of cloud contamination originating from high ice clouds. The residual cloud impact can have some drawbacks. 
At 183\,GHz, the impact of hydrometeors typically causes a decrease in the observed radiance due to scattering from ice hydrometeors (e.g.\ \citet{barlakas:three:20}). This implies that if any cloud contamination is missed by the filtering, a negative bias in mean radiance will result compared to the true clear-sky mean, which may translate into a bias in humidity after the retrieval or assimilation. For NWP systems assimilating clear-sky observations, the effect of undetected clouds may be overcome by inflating the observational errors and diminishing the impact of observations. Furthermore, the mathematical assumptions of data assimilation (DA) are predicated on Gaussian errors with no mean bias, and residual cloud impacts that cause a net bias are not easily handled by variational bias correction. One solution is to apply a very strict filtering, but this increases the rejection of clear-sky values, i.e.\ an important loss of useful data. Another limitation of existing clearing approaches is their ``one for all'' approach, i.e.\ observations in all 183\,GHz channels are either kept or rejected. This often rejects more observations than needed, as the channels differ in their altitude coverage. An observation could be cloudy in some channels and still the be clear-sky in others. To allow a channel specific filtering, data likely need to be combined in a more complex manner than simple differences, but it is unclear what type of regression would be best as the ideal solution would be scene-dependent. This points towards applying machine learning, as used by e.g.\ \citet{favrichon2019detecting}. A maybe less obvious problem is the assignment of uncertainty to the filtered values. To our best knowledge, so far only estimates of mean and worst case errors exist in the literature. Some cases with relatively high cloud impact will likely be missed, while most cases are clear-sky from the start. As the remaining cloudy cases can cause significant biases, the likely solution is to apply a quite conservative (high) error estimate. However, this will unnecessarily downgrade the value of the truly clear-sky cases and the observations are used in a non-optimal manner.

@@

The main focus of this study is the potential of this cloud-correction
method using sub-millimetre (sub-mm) observations, which will become available
operationally with the launch of the Ice Cloud Imager (ICI,
\citet{eriksson:towar:20}) on board the next generation of EUMETSAT Polar System - Second Generation (EPS-SG), but will likely also be included in
several smaller missions (such as Artic Weather Satellite (AWS); presented
below). Additionally, we demonstrate the feasibility of the approach based on
observations at 89 and 150\ GHz channels (following
\citet{geer2015scatteringindex}), which are available on several sensors extant today. The focus
on sub-mm channels is motivated by several reasons. First, the higher
frequencies are more sensitive to scattering effects from smaller
hydrometeors and are thus expected to provide greater sensitivity to high altitude cirrus clouds. For example, in some cloudy situations the
cloud impact at 183\,GHz may be of the order of thermal noise and modelling uncertainties,
while the impact at 325\,GHz is significant enough to provide sufficient signal to noise for identifying cloud. Second, the proposed
cloud correction methods allow integration of ICI sub-mm observations in
clear-sky DA schemes with no further modifications, thus providing a simple
way to make use this novel data source as soon as it becomes available.

@@

\section{Data and methods}
\label{data_methods}
%
\subsection{Satellite Instruments}
%
\subsubsection{ MicroWave Humidity Sounder-2}
%
%t
\begin{table}[t]
	\caption{Specifications of MWHS-2 channels relevant to this study.}
	\label{tab:specifications_MWHS2}	
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth & NE$\Delta$T \\
		& [GHz]			& [MHz]		& [K]		\\
		\middlehline
		1	&	89.0   		  & 1500			&	1.0	\\
		6	&	118.75±1.1    & \phantom{0}200 	&	1.6\\
		7	&	118.75±2.5    & \phantom{0}200 	&	1.6\\
		10	&	150.0         & 1500 			&	1.0 \\
		11	&	183.31±1.0      & \phantom{0}500  &	1.0 \\
		12  & 	183.31±1.8    & \phantom{0}700 	&   1.0\\
		13  & 	183.31±3.0      & 1000    		&	1.0	\\
		14  & 	183.31±4.5    & 2000    		&	1.0\\
		15  & 	183.31±7.0      & 2000  			&	1.0  \\
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}
The MicroWave Humidity Sounder 2 (MWHS-2) is an instrument on two current satellites in the FengYun-3 series, FY-3C and FY-3D. MWHS-2 a cross track scanning microwave radiometer and measures 15 frequencies in the range 89-191\,GHz. 89\,GHz and 150\,GHz are window channels, five humidity sounding channels are centered at 183.31\,GHz, and eight temperature sounding channels are centered on the 118.75\,GHz oxygen absorption line. The five humidity sounding channels are similar to ATMS. Observations from MWHS-2 are routinely assimilated in all-sky conditions at the European Centre for Medium-Range Weather Forecasts (ECMWF) with demonstrable positive impact on forecast performance \citep{duncan2020MWHS}. The channels relevant to this study are described in Table~\ref{tab:specifications_MWHS2}.

@@

\subsubsection{Ice Cloud Imager}
%
%t
\begin{table}[t]	
	\caption{Specifications of ICI channels relevant to this study.}
	\label{tab:ICI_MWI_channels}
	\begin{tabular}{crrr}
		\tophline
		Channel & Frequency 	& Bandwidth  	&NE$\Delta$T	\\
				& [GHz]			& [MHz]			& [K]			\\
		\middlehline
		I1V&	183.31$\pm$7.0    & 2000 			& 0.8 		\\
		I2V&	183.31$\pm$3.4    & 1500 			& 0.8 		\\
		I3V&	183.31$\pm$2.0    & 1500			& 0.8 		\\
		I5V&	325.15$\pm$9.5    & 3000			& 1.2 		\\
		I6V&	325.15$\pm$3.5    & 2400			& 1.3 		\\
		I6V&	325.15$\pm$1.5    & 1600			& 1.5 		\\
		I8V&	448.00$\pm$7.2    & 3000			& 1.4 		\\
		I9V&	448.00$\pm$3.0    & 2000			& 1.6 		\\
		I10V&	448.00$\pm$1.4    & 1200			& 2.0 		\\
		I11V&	664.00$\pm$4.2    & \phantom{0}500	& 1.6 		\\		
		\bottomhline
	\end{tabular}
	\belowtable{} % Table Footnotes
\end{table}

The Ice Cloud Imager (ICI) is a new instrument on board EPS-SG satellite MetOp-SG (Meteorological Operational - Second Generation). MetOp-SG is scheduled for launch in 2023, and it will make ICI the first operational sensor observing Earth using sub-mm wavelengths. The main objective of ICI is to use high frequency channels for measuring ice cloud properties, and improve the representation of ice clouds in regional and global NWP models. ICI is a conically scanning radiometer that will measure 13 frequencies from 183\,GHz up to 664\, GHz.  Among all available channels, 183.31\,GHz, 325.15\,GHz and 448.00\,GHz, will measure vertical polarization;  while other channels around frequencies 243.20\,GHz and 664.00\,GHz are ``window channels'' and will measure both vertical and horizontal polarization. The instrument will observe earth from a mean altitude of 832\,km with sensor viewing angle 44.767$^\unit{^{\degree}}$(measured from nadir). For all the channels, the mean footprint size is about 15\,km, but the exact geo-location of samples differs. Therefore, a simultaneous utilization of data from different channels shall require remapping to a common footprint \citep{eriksson:towar:20}.

@@

ICI and AWS frequencies are simulated with Atmospheric Radiative Transfer Simulator (ARTS, \citet{buehler:artst:18}). CloudSat \citep{Stephens2002cloudsat} profiles during August 2015 are randomly selected for forward simulations. The input data are restricted between $60\unit{^{\degree}S}$ to $60\unit{^{\degree}N}$, and surface is below 500\,m. Both clear-sky and all-sky scenarios  are simulated. The complete simulation setup is described in Appendix \ref{appendix:ARTS_setup}. For ICI and AWS, 220\,000 and 143\,000 cases are simulated, respectively. All AWS sensor viewing angles (from $0^{\degree}$ to $45^{\degree}$) are simulated, but the results described in this study are based on nadir viewing angle. Simulations for all three sensors are noise free, so to incorporate the measurement uncertainties, whenever needed, gaussian noise is added to according to the channel NE$\Delta$T (see Table~\ref{tab:specifications_MWHS2} - Table~\ref{tab:specifications_AWS}).

The simulations are split into training and testing datasets. The training dataset is used to train the machine learning model, while the testing dataset is used to evaluate the trained model. The construction and details of the model are described in Sect.~\ref{sec:QRNN}. For MWHS-2, 220\,000 simulations are randomly selected as training dataset, while 70\,000 are used for testing. For ICI, 175\,000 cases are randomly picked to form the training set. The remaining 45\,000 are used for testing. A smaller database is selected for AWS. 120\,000 simulations are used for training and the rest for testing.

@@

	\item QRNN-all: Same as QRNN-single, but all available 183\,GHz channels are included.      
\end{enumerate}

@@

All evaluation results except hyper-parameter tuning, described in the study, have been made on the test dataset. The hyper-parameter tuning is made on the validation dataset (see Appendix~\ref{appendix:hyperparamter}). The validation dataset is part of the training dataset which is held back during the training.

@@

\subsubsection{QRNN-single applied to MWHS-2 channel 14} 
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/QRNN_output_mwhs.pdf} 
	\caption{The distribution of point estimate obtained from QRNN-single 89+150\,GHz for MWHS-2 channel 14. The corresponding distributions for all-sky and clear-sky simulations are also shown.}
	\label{fig:distribution_predicted_mwhs14}	
\end{figure}
\begin{figure}[t]
	\centering
	\includegraphics[width = 70mm]{Figures/MWHS_error_dist_14.pdf} 
	\caption{The error distribution for deviations of point estimates to NFCS simulations. The results are from QRNN-single experiment 89+150\,GHz and MWHS-2 channel 14. Noise is also plotted for reference. The label ``All-sky'' represents the all-sky simulations, ``Predicted(All)'' denotes the predicted point estimates. The error distribution achieved with scattering index (SI) filtering is also shown (Filtered(SI)). }
	\label{fig:error_distribution_mwhs14}	
\end{figure}
\begin{table*}[t]
	\caption{The error statistics for deviations of point estimates to NFCS simulations. Results are for different QRNN experiments for MWHS-2 channel 14 (see Sect.~\ref{sec:QRNN_expt_MWHS}). The statistics for all-sky and clear-sky simulations are also provided. The label ``All'' denotes the entire dataset of predicted point estimates, while ``Pred.(5\,K)'' refers to the predicted point estimates but where cases with cloud correction greater than 5\,K are excluded. The last two columns show the statistics obtained after filtering cloudy cases according to scattering index (SI) and scheme by \citet{buehler:aclou:07} (B183). Bias, MAE, STD are in K, skewness is dimensionless.}
	\label{tab:error_statistics_mwhs_14}
	\setlength{\tabcolsep}{4pt}
	\begin{tabular}{lrr|rr|rr|rr|rr|rr}
		\tophline
		&\multicolumn{2}{c|}{Simulations}& \multicolumn{6}{c|}{QRNN-single} & \multicolumn{2}{c|}{QRNN-all} & \multicolumn{2}{c}{Pure filtering}\\
		\cline{2-13}
		%		\hline
		&   Clear-sky &   All-sky &  \multicolumn{2}{c|}{89+150\,GHz} & \multicolumn{2}{c|}{89+150+118\,GHz} & \multicolumn{2}{c|}{150\,GHz} & \multicolumn{2}{c|}{89+150+183\,GHz}& SI & B183\\		
		&			   &			& All & Pred.(5\,K) & All & Pred.(5\,K) & All & Pred.(5\,K)  & All & Pred.(5\,K)&&\\
		\middlehline
Bias     &  0.00 &  -0.84 & -0.10 & -0.09 & -0.05 & -0.04 & -0.11 & -0.10 & -0.10 & -0.09 & 0.24  & -0.52\\
MAE      &  0.80 &   1.45 &  0.89 &  0.87 &  0.90 &  0.88 &  0.90 &  0.88 &  0.62 &  0.60 & 0.92  & 1.15\\
STD      &  1.00 &   3.73 &  1.20 &  1.16 &  1.21 &  1.16 &  1.22 &  1.18 &  0.91 &  0.85 & 1.26  & 1.86\\
Skewness & -0.02 & -12.72 & -1.17 & -1.00 & -1.06 & -0.90 & -1.16 & -1.04 & -1.78 & -1.71 &-1.95  & -3.45\\
Rejection&  -	 & - 	  & - 	  & 3.3\% & - 	  & 3.4\% & -     & 3.2\% & -     & 3.3\% & 28.8\%& 3.5\%\\
\bottomhline
	\end{tabular}
\end{table*}

The posterior distribution of $\ynfcs$ obtained from experiment 89+150\,GHz is similar to the one shown in Fig.~\ref{fig:posterior_distribution_I1V} and the distribution of point estimates is displayed in Fig.~\ref{fig:distribution_predicted_mwhs14}. The predicted values are able to correct most of the low brightness temperature cases, and overall a good match with the NFCS simulations is observed. However, QRNN is unable to predict the lowest clear-sky brightness temperatures, and cases with brightness temperatures around 260\,K occur frequently. The deviations of point estimates to NFCS simulations are shown in Fig.~\ref{fig:error_distribution_mwhs14}. The large negative deviations are removed (blue curve), but residual cloud impact is evident in the negative tail. Most of these residual cases have departures less than 10\,K. The appearance of a small positive tail also indicates overestimation in few cases. The corresponding error statistics(see Sect.~\ref{sec:validation}) are provided in  Table~\ref{tab:error_statistics_mwhs_14}. In the uncorrected all-sky simulations, the negative departures due to cloud impact lead to a large negative skewness(-12.72) and high bias (-0.84\,K). QRNN trained with 89 and 150\,GHz successfully corrects a major portion of the cloud affected cases, and the bias is reduced to -0.10\,K. However, negative skewness indicates presence of  uncorrected departures. Including 118\,GHz in the training gives comparable results as 89+150\,GHz. The error distribution has lower bias and are more symmetric, but the MAE and standard deviation remain unaltered. This indicates that the information from 118\,GHz channels can be beneficial in predicting few cases correctly, but the overall consequence is not exceptionally different from 89+150\,GHz. Similar is the case with using only 150\,GHz---the differences between the three experiments are negligible.

Further, we investigate whether filtering the predictions with low accuracy could help in improving the error distributions. For filtering such cases, we assume that predictions with cloud correction greater than 5\,K are associated with large deviations. In all three experiments, removing the cases with correction greater than 5\,K removes around 3\% of the data, but only a marginal positive impact on the accuracy is observed. The persistent negative skewness indicates presence of cases with residual cloud impact. Such cases are most likely to be associated with low cloud impact. Choosing a lower threshold can help in removing more partially corrected cases but at the cost of rejecting clear-sky cases. Since QRNN gives out NFCS values, choosing an unusually low correction threshold can also classify noisy clear-sky cases as cloudy. For example, for 89+150\,GHz, a threshold of 1.5\,K rejects almost 10\% of data, but the negative skewness is still not completely removed.

In spite of the fact that QRNN only provides a partial cloud correction, the results for  MWHS-2 channel 14 are comparable to what we achieve with existing cloud filtering techniques like scattering index (SI) and the filtering scheme by \citet{buehler:aclou:07}. SI uses the differences of brightness temperatures between 89 and 150\,GHz to identify cloud affected data, whilst in the study by \citet{buehler:aclou:07}, they use brightness temperature based threshold to filter out cloudy cases. They recommend a viewing angle dependent brightness temperature threshold at $183.31\pm1.00$ \,GHz and brightness temperature difference between $183.31\pm3.00$ \,GHz and $183.31\pm 1.00$ \,GHz as a measure of cloud impact. Further in the text we refer this filter as ``B183''. The results obtained with SI and B183 are displayed in last two columns of Table~\ref{tab:error_statistics_mwhs_14}. With SI threshold = 5\,K, almost 28\% of the data is rejected, yet the resulting error distributions are poorer as compared to QRNN. The low bias and skewness values indicate that most of the high negative departures are removed, but cases with low cloud impact pass the filter as clear. Similar is the case with B183. Here only 3\% of the data is filtered out but the overall statistics are worse than both QRNN and SI. The results from the two filters are not surprising as both are partial filters and aim at removing only cases with high ice content. The low hydrometeor impact cases remain unaltered.

The three experiments were also performed for other four 183\,GHz channels, and a similar performance was obtained (Table not shown). The positive effect of 118\,GHz was slightly higher for MWHS-2 channel 15, but for others, no notable effect was observed. In view of negligible performance differences between the three experiments, we consider the combination 89+159\,GHz to be the optimal. The results for other channels with this experiment are provided in Sect.~\ref{sec:mwhs_others}

\subsubsection{Comparison of QRNN-all and QRNN-single}
%
%f
\begin{figure}[t]
	\centering
	\includegraphics[height=45mm]{Figures/correlation.pdf} 
	\caption{ The triangular error correlation matrix obtained from QRNN-single and QRNN-all for MWHS-2. The label ``Clear'' represents cases with cloud impact less than 2\,K.}
	\label{fig:correlations_mwhs}	
\end{figure}
To assess the differences between the capabilities of QRNN-all against QRNN-single, we  compare the error statistics obtained for 89+150\,GHz and 89+150+183\,GHz for channel 14.  Table~\ref{tab:error_statistics_mwhs_14} also shows the error statistics for the experiment QRNN-all. In comparison to QRNN-single, we obtain almost similar error bias with QRNN-all, but the MAE and standard deviation reduce by almost 30\% and 24\% respectively. However, the negative tail becomes more prominent. The low standard deviation, but strong negative tail indicates that the narrow spread is a consequence of correction of noise in clear-sky cases. Since a majority of the cases are clear-sky, their impact dominates the whole statistics. In order to probe the positive effect of QRNN-all, we also estimate the errors for all cases with cloud correction greater than 5\,K (table not shown). For such cases,  QRNN-all has slightly better accuracy than QRNN-single.   The bias in QRNN-all and standard deviation is -0.53\,K and 1.93\,K, respectively, in comparison to -0.61\,K and 2.04\,K as observed in QRNN-single. Thus, the concurrent use of all 183\,GHz channels can provide additional information on cloud structures to QRNN.
